Who needs privacy? Exploring the relations between need for privacy and personality

### 2024-02-07 analyses.RmD
- Collected and analzed data - Wrote results and discussion section

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 90)
```

@@

- At this point, we haven't yet collected data. 
- The results below use simulated data. 
- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit or imputation of missing data.

# Set-Up

@@

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse", "td")

# load packages
lapply(packages, library, character.only = TRUE)

# readability function
readability = function(data){
  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
  textstat_readability(data, measure = reading_estimates) %>% 
    as.data.frame %>% 
    mutate(average = rowMeans(select(., -document)))
}
```

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
d <- rename(d, COL = COL_, REL = REL_)

# define vars and labels
vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", 
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
                   "HEX_ALT")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
                       "Altruism")

@@

vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Social", "Physical", "Psychological",
                  "Companies", "Governnment",
                  "Anonynmity", "Infornmational", "General")
vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
                  "Companies", "Govern-\nment",
                  "Anony-\nmity", "Infor-\nmational", "General")
vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
                  "Comp.", "Gov.",
                  "Anonym.", "Inform.", "General")

vars_ses <- c("AGE", "GEN", "ETH", "REL", "COL", "INC", "CON")
vars_ses_txt <- c("Age", "Gender", "Ethnicity", "Relationship", "College", "Income", "Conservatism")
```

@@

@@

```{r}
name <- "HEX_HOH_SIN"
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_HOH_FAI"
model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEY_HOH_GRE"
model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_HOH_MOD"
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

```{r}
name <- "HEX_EMO_FEA"
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

@@

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
 4.	I hate it when people enter my personal space uninvited.

>>>>

```{r knitr-setup, include=F}
set.seed(170819)

knitr::opts_chunk$set(
  warning=F, 
  echo=F, 
  error=F, 
  message=F, 
  cache = T, 
  tidy=T, 
  dev = 'pdf', 
  cache.extra = knitr::rand_seed
  )

options(
  digits = 3, 
  width = 150,
  max.print = 100000000
  )
```

@@

# Set-Up
## Packages

@@

library(confintr)
library(corrplot)
library(devtools)
library(easystats)
library(GGally)
library(ggplot2)
library(haven)
library(kableExtra)
library(knitr)
library(lavaan)
library(magrittr)
library(mice)
library(MVN)
library(naniar)
library(PerFit)
library(psych)
library(quanteda.textstats)
library(pwr)
library(semPlot)
library(sjlabelled)
library(simsem)
library(semTools)
library(tidyverse)
library(td)

load("data/workspace_1.RData")
source("custom_functions.R")
```

```{r data-wrangling}
# d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
d_raw <- sjlabelled::read_spss(
  "data/Need+for+Privacy_February+6%2C+2024_15.56.sav",
  convert.factors = FALSE
  )
```

### Data-Wrangling

```{r data-inverting}
vars_invert <- c(
  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
  "HEX_EMO_SEN_04",
  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
  "HEX_EXT_SOC_01",
  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
  "HEX_AGR_GEN_01",
  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
  "HEX_CNS_PER_02",
  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
  "HEX_ALT_03", "HEX_ALT_04",
  "NFP_COM_02"
)

d <-
  d_raw %>% 
  rename(
    COL = COL_,
    REL = REL_
    ) %>%
  mutate(
    across(all_of(vars_invert),
    ~ 8 - .x
         ),
    male = case_match(
      GEN,
      c(2, 3) ~ 0,
      1 ~ 1),
    age = case_match(
      AGE,
      1 ~ 1,
      2 ~ 2,
      3 ~ 3,
      4 ~ 4,
      5 ~ 7,
      6 ~ 5,
      7 ~ 6),
    white = case_match(
      ETH,
      2 ~ 0,
      1 ~ 1),
    relation = case_match(
      REL,
      2 ~ 1,
      1 ~ 0),
    college = case_match(
      COL,
      2 ~ 1,
      1 ~ 0),
    conserv = CON,
    income = INC
  ) 
```

### Labels

```{r data-labels}
# define vars and labels
vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")

vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
                   "HEX_ALT",
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Altruism",
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality")

vars_pers_hoh <- 
  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
vars_pers_emo <- 
  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
vars_pers_ext <- 
  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
vars_pers_agr <- 
  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
vars_pers_cns <- 
  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
vars_pers_opn <- 
  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")

vars_pers_all <- 
  c(
    vars_pers_hoh, 
    vars_pers_emo, 
    vars_pers_ext, 
    vars_pers_agr, 
    vars_pers_cns,
    vars_pers_opn
    )

vars_pers_all_txt <- 
  c("Honesty humility", 
      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
    "Emotionality", 
      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
    "Extraversion",
      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
    "Agreeableness",
      "Forgiveness", "Gentleness", "Flexibility", "Patience",
    "Conscientiousness",
      "Organization", "Diligence", "Perfectionism", "Prudence", 
    "Openness",
      "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
    )

vars_pred_all_txt <- 
  c(
    vars_pers_all_txt,
    vars_ses_txt
    )

@@

vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
              "NFP_GOV", "NFP_COM", 
              "NFP_INF", "NFP_ANO", "NFP_GEN")
vars_pri_txt <- c("Psychological", "Social", "Physical", 
                  "Government", "Companies", 
                  "Informational", "Anonymity", "General")
vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
                  "Govern-\nment", "Companies", 
                  "Infor-\nmational", "Anony-\nmity", "General")
vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
                  "Gov.", "Comp.", 
                  "Inform.", "Anonym.", "General")

vars_pers_pri <- c(vars_pers_fac, vars_pri)
```

## Means

```{r}
# Person means per facet

d %<>%
  mutate(
    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
  )

# item means
c_m <- 
  c(
    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
  )

# item standard deviation
c_sd <- 
  c(
    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
  )
```

# Missing data

First filter those who didn't finish the questionnaire.

```{r}
d %<>%
  filter(
    Progress == 100
  )

n_finished <- nrow(d)
```

Let's first inspect missing data.

How many missing do we have?

```{r}
n_miss(d)
prop_miss(d)
```

Only 23 cells are missing -- which is very little. To be precise, 0.00006 percent only.

Which variables are affected?

```{r}
miss_var_summary(d) %>% 
  head(19)
```

Missing answers vary randomly across variables.

How about participants?

```{r}
miss_case_summary(d)
```

Only six participants with missing data, and even then, not much. We hence decided to keep everyone.

# Quality checks

We preregistered to remove participants faster than 3 standard deviations than the median response time.

```{r cache=F}
# Median response time
time_med <- median(d$Duration__in_seconds_)

# Average response time
time_m <- mean(d$Duration__in_seconds_) / 60

# Standard deviation
time_sd <- sd(d$Duration__in_seconds_)

# filter speeders
time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
```

However, this made little sense. The median response time was `r time_med` and the standard deviation `r time_sd`. Hence, three SDs below median was `r time_crit_init`, hence not informative.

Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.

```{r cache=F}
time_crit <- 5 * 60

# count number of speeders
n_speeding <- 
  nrow(
    filter(
      d, 
      Duration__in_seconds_ < time_crit
      )
    )

# Deletion of fast respondents
d <- 
  filter(
    d, 
    Duration__in_seconds_ >= time_crit
    )

n_used <- nrow(d)
```

Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.

Let's inspect for potential response patterns.

# Sociodemographics

To improve privacy, we didn't collect exact but binned measures of sociodemographics.

Let's first inspect age. Here, the age categories were as follows:

1: Under 18 years old
2: 18-24 years old 
3: 25-34 years old 
4: 35-44 years old 
5: 45-54 years old 
6: 55-64 years old 
7: 65+ years old

```{r}
table(d$AGE)
```

No person indicated being younger than 18 years old. Hence, everybody could be included.

```{r}
age_m <- 
  mean(d$AGE)
```

The mean age was 45 to 54 years of age.

Let's next inspect gender. Categories were:

1: "Man" 
2: "Woman" 
3: "Third gender / Other"

```{r}
table(d$GEN) %>% 
  prop.table() %>% 
  round(2)
```

48 percent were male, 50 female, and 1 percent indicated third/other gender.

Let's next inspect education. Categories were:

1: "No college degree" 
2: "College degree"

```{r}
table(d$COL) %>% 
  prop.table() %>% 
  round(2)
```

69% reported having a college degree.

Let's next inspect ethnicity. Answer categories were as follows:

1: "White"
2: "Other"

```{r}
table(d$ETH) %>%
  prop.table() %>% 
  round(2)
```

78 % percent were white, 22 % not white.

@@

## Ceiling/Floor effects

Let's first check for ceiling and floor effects.

```{r}
d %>%
  select(
    paste0(rep(vars_pers_pri, each = 4), "_0", 1:4)
  ) %>% 
  apply(
    2,  mean, na.rm = T
  )
```

No item below floor (1.5) or ceiling (6.5) thresholds.

@@

```{r}
name <- "HEX_HOH_SIN"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is okay, but RMSEA is significantly above .10. Let's hence inspect modification indices to see if there are potential fixes.

```{r}
modindices(fit_HEX_HOH_SIN)
```

Suggests that item 1 & 3, and item 2 & 4 build subdimensions. Let's allow covariances.

```{r}
model <- 
  "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
  HEX_HOH_SIN_01 ~~ a*HEX_HOH_SIN_03
  HEX_HOH_SIN_02 ~~ a*HEX_HOH_SIN_04
"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is now great.

@@

```{r}
name <- "HEX_HOH_FAI"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}

model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is good.

@@

```{r}
name <- "HEX_HOH_GRE"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}

model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is okaish, but RMSEA above .10. Let's inspect modification indices.

```{r}
modindices(fit_HEX_HOH_GRE)
```

Item 1 & 2, and item 3 & 4 form subdimensions.

```{r}
model <- "
  HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
  HEX_HOH_GRE_01 ~~ a*HEX_HOH_GRE_02
  HEX_HOH_GRE_03 ~~ a*HEX_HOH_GRE_04
"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is now great.

@@

```{r}
name <- "HEX_HOH_MOD"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLM")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is good.

#### Honesty Humility

Let's also look at the dimension itself.

```{r}
model_hex_hoh <- "
# Personality Factors
HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04

# Covariances
HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
"
fit_hex_hoh <- sem(model_hex_hoh, d, estimator = "MLM", fixed.x = TRUE)
summary(fit_hex_hoh, standardized = TRUE, fit = TRUE)
```

@@

```{r}
name <- "HEX_EMO_FEA"

plot_hist(name)

mardia(
  select(
    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
  )
)
```

Assumption of multivariate normality violated. Hence we'll use the robust estimator.

```{r}
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"

assign(
  paste("fit", name, sep = "_"), 
  cfa(model, d, estimator = "MLR", missing = "FIML")
  )

summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
```

Fit is great.

@@

 1.	I don’t like it when strangers come too close to me.
 2.	I don’t like to stand in a dense crowd of people.
 3.	I don’t like to sit next to a stranger on a train, bus, or plane.
 4.	I hate it when people enter my personal space uninvited.

```{r}
name <- "NFP_PHY"

plot_hist(name)
